---
title: "Overlap in friends’ lists"
output: html_document
---

We first install the latest versions of the needed R packages.

```{r, eval=FALSE}
devtools::install_github("rstudio/leaflet")
devtools::install_github("rturn/parseTweetFiles")
devtools::install_github("SMAPPNYU/smappR")
devtools::install_github("pablobarbera/streamR/streamR")
```

We load the packages and set knitr options.


```{r}
library(smappR)
library(streamR)
library(knitr)
opts_chunk$set(cache.extra = list(R.version, sessionInfo(), format(Sys.Date(), '%Y-%m')))
```

Now, we get the list of followers of WaleedGaj2002.

```{r wg-followers, cache=TRUE}
fols<- getFollowers(screen_name="WaleedGaj2002", oauth_folder = "~/Dropbox/credentials", sleep=65)
length(fols)
```

Now that we've the list of followers of WaleedGaj2002, we can randomly choose two followers and calculate the Jaccard index for their friends lists.

Recall that Jaccard index for nodes i and j is $$J(i,j) = \frac{|A \cap B|}{|A \cup B|}$$ where node i has friends list A and B denotes the friends list of node j.






```{r}
samp<- sample(fols, size =2, replace=FALSE)

calc_jaccard <- function(id1, id2, sleep = 10){
    fol1 <- NA
    fol2 <- NA
    try(fol1 <- getFollowers(user_id=id1, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    try(fol2 <- getFollowers(user_id=id2, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    denom <- length(union(fol1, fol2))
    num <- length(intersect(fol1, fol2))
    ratio <- num/denom
    return(list(ratio=ratio, num=num, denom=denom, n1 = length(fol1), n2=length(fol2)))
}

calc_jaccard(id1=samp[1], id2 = samp[2], sleep=100)

samp_jaccard <- function(followers=fols){
    samp <- sample(followers, size = 2, replace=FALSE)
    ji<- calc_jaccard(id1=samp[1], id2 = samp[2], sleep=100)
    return(list(ji, id1 = samp[1], id2=samp[2]))
}

```


```{r loop}
replicate(expr = samp_jaccard(fols), n=25)



```

