---
title: "Overlap in friends’ lists"
output: html_document
---

We first install the latest versions of the needed R packages.

```{r, eval=FALSE}
devtools::install_github("rstudio/leaflet")
devtools::install_github("SMAPPNYU/smappR")
devtools::install_github("pablobarbera/streamR/streamR")
```

We load the packages and set knitr options.


```{r}
library(smappR)
library(streamR)
library(knitr)
opts_chunk$set(cache=TRUE, cache.extra = list(R.version, sessionInfo(), format(Sys.Date(), '%Y-%m')))
```

Now, we get the list of followers of \@WaleedGaj2002 and \@saeed_950. 

```{r seed-fol-fr, cache=TRUE}
fr1 <- getFriends(screen_name = "WaleedGaj2002", oauth_folder = "~/Dropbox/credentials", sleep=60)
fr2 <- getFriends(screen_name = "saeed_950", oauth_folder = "~/Dropbox/credentials", sleep=60)
fol1 <- getFollowers(screen_name = "WaleedGaj2002", oauth_folder = "~/Dropbox/credentials", sleep=60)
fol2 <- getFollowers(screen_name = "saeed_950", oauth_folder = "~/Dropbox/credentials", sleep=60)
```

Now that we've the list of followers and friends of \@WaleedGaj2002 and \@saeed_950, let's look at their overlap. 


Recall that Jaccard index for nodes i and j is $$J(i,j) = \frac{|A \cap B|}{|A \cup B|}$$ where node i has friends list A and B denotes the friends list of node j.






```{r, cache=TRUE}
calc_jaccard<- function(a,b){
    denom <- length(union(a, b))
    num <- length(intersect(a, b))
    ratio <- num/denom
    out<- list(jaccard=ratio, numerator=num, denominator=denom)
    return(out)
}

jac_wrap <- function(id1, id2, sleep = 60, fn1 = getFriends, fn2=getFriends){
    f1 <- NA
    f2 <- NA
    try(f1 <- fn1(user_id=id1, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    try(f2 <- fn2(user_id=id2, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    ji <- calc_jaccard(f1, f2)
    return(list(ji, f1=f1, f2=f2))
}


```

## Counting overlap in friends of \@WaleedGaj2002 and friends of \@saeed_950


```{r overlaps, cache=TRUE}
intersect(fr1, fr2)
intersect(fr1, fol1)
intersect(fr1, fol2)
intersect(fr2, fol1)
intersect(fr2, fol2)
intersect(fol1, fol2)

length(intersect(fr1, fr2))
length(intersect(fr1, fol1))
length(intersect(fr1, fol2))
length(intersect(fr2, fol1))
length(intersect(fr2, fol2))
length(intersect(fol1, fol2))

calc_jaccard(fr1, fr2)
calc_jaccard(fr1, fol1)
calc_jaccard(fr1, fol2)
calc_jaccard(fr2, fol1)
calc_jaccard(fr2, fol2)
calc_jaccard(fol1, fol2)
```

Let's get the user information for the two seeds.

```{r seed-info}
seed_info<- getUsers(oauth_folder = "~/Dropbox/credentials/", screen_names = c("WaleedGaj2002", "saeed_950"))
seed_info
```

## Who are the eight users that both \@WaleedGaj2002 and \@saeed_950 follow?

```{r overlap-fr1-fr2}
foo <- getUsers(id = intersect(fr1, fr2), include_entities = TRUE, verbose = TRUE, oauth_folder = "~/Dropbox/credentials/")

extract_user_info <- function(user_list){
    out <- list(id=user_list$id, name=user_list$name, screen_name=user_list$screen_name, location=user_list$location, description=user_list$description, followers_count=user_list$followers_count, friends_count=user_list$friends_count, created_at = user_list$created_at)
    return(out)
}

```






```{r}
bar <- sapply(FUN=extract_user_info, X=foo)
kable(data.frame(t(bar)))
```



### Session info

```{r}
devtools::session_info()
```

