---
title: "Overlap in friends’ lists"
output: html_document
---

We first install the latest versions of the needed R packages.

```{r, eval=FALSE}
devtools::install_github("rstudio/leaflet")
devtools::install_github("SMAPPNYU/smappR")
devtools::install_github("pablobarbera/streamR/streamR")
```

We load the packages and set knitr options.


```{r}
library(smappR)
library(streamR)
library(knitr)
opts_chunk$set(cache.extra = list(R.version, sessionInfo(), format(Sys.Date(), '%Y-%m')))
```

Now, we get the list of followers of WaleedGaj2002.

```{r wg-followers, cache=TRUE}
# fols<- getFollowers(screen_name="WaleedGaj2002", oauth_folder = "~/Dropbox/credentials", sleep=65)
#length(fols)
fr1 <- getFriends(screen_name = "WaleedGaj2002", oauth_folder = "~/Dropbox/credentials", sleep=60)
fr2 <- getFriends(screen_name = "saeed_950", oauth_folder = "~/Dropbox/credentials", sleep=60)
```

Now that we've the list of followers of WaleedGaj2002, we can randomly choose two followers and calculate the Jaccard index for their friends lists.

Recall that Jaccard index for nodes i and j is $$J(i,j) = \frac{|A \cap B|}{|A \cup B|}$$ where node i has friends list A and B denotes the friends list of node j.






```{r}

calc_jaccard_followers <- function(id1, id2, sleep = 10){
    fol1 <- NA
    fol2 <- NA
    try(fol1 <- getFollowers(user_id=id1, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    try(fol2 <- getFollowers(user_id=id2, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    denom <- length(union(fol1, fol2))
    num <- length(intersect(fol1, fol2))
    ratio <- num/denom
    return(list(ratio=ratio, num=num, denom=denom, n1 = length(fol1), n2=length(fol2)))
}


samp_jaccard_followers <- function(followers=fols){
    samp <- sample(followers, size = 2, replace=FALSE)
    ji<- calc_jaccard_followers(id1=samp[1], id2 = samp[2], sleep=100)
    return(c(unlist(ji), samp[1], samp[2]))
}
calc_jaccard_friends <- function(id1, id2, sleep = 10){
    fol1 <- NA
    fol2 <- NA
    try(fol1 <- getFriends(user_id=id1, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    try(fol2 <- getFriends(user_id=id2, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    denom <- length(union(fol1, fol2))
    num <- length(intersect(fol1, fol2))
    ratio <- num/denom
    return(list(ratio=ratio, num=num, denom=denom, n1 = length(fol1), n2=length(fol2)))
}


samp_jaccard_friends <- function(friends=frs){
    samp <- sample(friends, size = 2, replace=FALSE)
    ji<- calc_jaccard_friends(id1=samp[1], id2 = samp[2], sleep=70)
    return(c(unlist(ji), samp[1], samp[2]))
}

```

```{r}
calc_jaccard<- function(a,b){
    denom <- length(union(a, b))
    num <- length(intersect(a, b))
    ratio <- num/denom
    return(ratio)
}

wrap <- function(id1, id2, sleep = 30){
    f1 <- NA
    f2 <- NA
    try(f1 <- getFriends(user_id=id1, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    try(f2 <- getFriends(user_id=id2, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    ji <- calc_jaccard(f1, f2)
    return(c(ji, id1, id2))
}


```

```{r replicate}
set.seed(2015-11-22)
replicate(expr = wrap(id1 = sample(fr1, size=1), id2 = sample(fr2, size=1)), n = 100)

save.image("tmp_RData/out-22-nov.RData")

```


```{r}
devtools::session_info()
```

