---
title: "Overlap in friends’ lists"
output: html_document
---

We first install the latest versions of the needed R packages.

```{r, eval=FALSE}
devtools::install_github("rstudio/leaflet")
devtools::install_github("SMAPPNYU/smappR")
devtools::install_github("pablobarbera/streamR/streamR")
```

We load the packages and set knitr options.


```{r}
library(smappR)
library(streamR)
library(knitr)
opts_chunk$set(cache=TRUE, cache.extra = list(R.version, sessionInfo(), format(Sys.Date(), '%Y-%m')))
```

Now, we get the list of followers of \@WaleedGaj2002 and \@saeed_950. 

```{r seed-fol-fr, cache=TRUE}
fr1 <- getFriends(screen_name = "WaleedGaj2002", oauth_folder = "~/Dropbox/credentials", sleep=60)
fr2 <- getFriends(screen_name = "saeed_950", oauth_folder = "~/Dropbox/credentials", sleep=60)
fol1 <- getFollowers(screen_name = "WaleedGaj2002", oauth_folder = "~/Dropbox/credentials", sleep=60)
fol2 <- getFollowers(screen_name = "saeed_950", oauth_folder = "~/Dropbox/credentials", sleep=60)
```

Now that we've the list of followers and friends of \@WaleedGaj2002 and \@saeed_950, let's look at their overlap. 


Recall that Jaccard index for nodes i and j is $$J(i,j) = \frac{|A \cap B|}{|A \cup B|}$$ where node i has friends list A and B denotes the friends list of node j.






```{r}

calc_jaccard_followers <- function(id1, id2, sleep = 10){
    fol1 <- NA
    fol2 <- NA
    try(fol1 <- getFollowers(user_id=id1, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    try(fol2 <- getFollowers(user_id=id2, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    denom <- length(union(fol1, fol2))
    num <- length(intersect(fol1, fol2))
    ratio <- num/denom
    return(list(ratio=ratio, num=num, denom=denom, n1 = length(fol1), n2=length(fol2)))
}


samp_jaccard_followers <- function(followers=fols){
    samp <- sample(followers, size = 2, replace=FALSE)
    ji<- calc_jaccard_followers(id1=samp[1], id2 = samp[2], sleep=100)
    return(c(unlist(ji), samp[1], samp[2]))
}
calc_jaccard_friends <- function(id1, id2, sleep = 10){
    fol1 <- NA
    fol2 <- NA
    try(fol1 <- getFriends(user_id=id1, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    try(fol2 <- getFriends(user_id=id2, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    denom <- length(union(fol1, fol2))
    num <- length(intersect(fol1, fol2))
    ratio <- num/denom
    return(list(ratio=ratio, num=num, denom=denom, n1 = length(fol1), n2=length(fol2)))
}


samp_jaccard_friends <- function(friends=frs){
    samp <- sample(friends, size = 2, replace=FALSE)
    ji<- calc_jaccard_friends(id1=samp[1], id2 = samp[2], sleep=70)
    return(c(unlist(ji), samp[1], samp[2]))
}

```

```{r, cache=TRUE}
calc_jaccard<- function(a,b){
    denom <- length(union(a, b))
    num <- length(intersect(a, b))
    ratio <- num/denom
    out<- c(ratio, num, denom)
    names(out)<- c("jaccard_index", "intersect_length", "union_length")
    return(out)
}

wrap <- function(id1, id2, sleep = 30){
    f1 <- NA
    f2 <- NA
    try(f1 <- getFriends(user_id=id1, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    try(f2 <- getFriends(user_id=id2, sleep=sleep, oauth_folder = "~/Dropbox/credentials"))
    ji <- calc_jaccard(f1, f2)
    return(ji)
}


```

## Counting overlap in friends of \@WaleedGaj2002 and friends of \@saeed_950


```{r overlaps, cache=TRUE}
intersect(fr1, fr2)
intersect(fr1, fol1)
intersect(fr1, fol2)
intersect(fr2, fol1)
intersect(fr2, fol2)
intersect(fol1, fol2)

length(intersect(fr1, fr2))
length(intersect(fr1, fol1))
length(intersect(fr1, fol2))
length(intersect(fr2, fol1))
length(intersect(fr2, fol2))
length(intersect(fol1, fol2))

calc_jaccard(fr1, fr2)
calc_jaccard(fr1, fol1)
calc_jaccard(fr1, fol2)
calc_jaccard(fr2, fol1)
calc_jaccard(fr2, fol2)
calc_jaccard(fol1, fol2)
```

Let's get the user information for the two seeds.

```{r seed-info}
seed_info<- getUsers(oauth_folder = "~/Dropbox/credentials/", screen_names = c("WaleedGaj2002", "saeed_950"))
seed_info
```

### Session info

```{r}
devtools::session_info()
```

